Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-10-04 ms.tex
added false alarm levels to periodograms.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{pc1_periodogram.pdf}
\includegraphics[width=0.49\textwidth]{pc2_periodogram.pdf}
\caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
\deleted{The first peak at 0.654 days for both principal components is the orbital period, which is the sampling cadence of the principal components' time series.}
PC$_1$ \deleted{also} peaks at 22.9, 153 and 750 days.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
The second principal components shows one dominant peak at 491 days, \deleted{in addition to the 0.654 orbital period,} indicating possible long term evolution of the dust particle sizes.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{pc1_periodogram.pdf}
\includegraphics[width=0.49\textwidth]{pc2_periodogram.pdf}
\caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
\deleted{The first peak at 0.654 days for both principal components is the orbital period, which is the sampling cadence of the principal components' time series.}
PC$_1$ \deleted{also} peaks at 22.9, 153 and 750 days.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
The second principal components shows one dominant peak at 491 days, \deleted{in addition to the 0.654 orbital period,} indicating possible long term evolution of the dust particle sizes.
\added{False alarm levels with probabilities of 0.05 and $10^{-4}$ are shown as orange horizontal lines.}}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}
